

\begin{abstract}
    % Motivation
    % Radiomics is the field of medicine where high amounts of quantitative features is
    % extracted from medical images. 
    % The field is most studied in terms of
    The goal in the field of radiomics is to establish
    links between diagnosis, prognosis and treatment response, from
    correlations in quantitative medical image features.
    % oncology, where features are aggregated in tumors. The goal is to establish
    % links between diagnosis, prognosis and treatment response, from
    % correlations in quantitative radiomics features. 
    Image modalities
    such as Positron Emission Tomography (PET) suffers from high feature
    variability inter scanners and due to different image reconstruction parameters.  
    Knowledge about how different parameters affects quantitative feature
    values is needed. 

    We will try to
    identify the features that are best able the separate different PET reconstruction
    method in a systematic way with the use of Support Vector Machine (SVM).

    Feature selection is an important step in the machine learning process because it helps to reduce the complexity of the 
    model, improve the accuracy of the model, reduce overfitting, reduce
    the training time of the model, increase explain ability of the model.  Feature selection helps 
    to identify the most important features that contribute to the prediction
    and discard the irrelevant or redundant features. 

    In the first part we will use random forest and correlation for feature
    selection to identify the features with best class separability between reconstruction.

    Then we will apply feed forward selection with Suport Vector Machine (SVM)
    to see if we are able to correctly predict the class targets. And also
    validate if or prior features selection agrees with the
    results obtained with SVM.         

    % TODO: main results
    % TODO: implications



    % Problem
    % In order for radiomics to have any clinical relevance, features values need
    % to be harmonized and standardized. A feature values should reflect the
    % underlying pathology and not vary due to scanner specific settings. It's
    % therefore important to establish how different scanner parameter affect the
    % feature value. If a link is established it may be possible to standardize
    % certain features.  


    % Especially in medicine it's important to be able to explain the outcomes of
    % a prediction.
    % What we have done

    % Our dataset contains 15 radiomics features extracted on 16 different lymphom
    % cancers acquired with a PET scanner. Each image is reconstructed with tree
    % different reconstruction methods (our class label targets). 

    % Implications
    % Try to establish models that maps recons?

\end{abstract}



